### 2020-02-24 RFCs/HDF5/VOL/connector_author_guide/appendix.tex
Updated VOL user guide and connector author guide to be in agreement with final 1.12.0 changes.
Former-commit-id: f656be3383755816b47e431b1dabfeb7ee3e402a

         & H5Oopen\_by\_addr \\

@@

@@

    get & N/A \\

@@

             & H5Ovisit\_by\_name2 \\

@@

             & H5Ovisit2 \\

@@

        & H5Lget\_info \\

@@

             & H5Literate \\
             & H5Literate\_by\_name \\
             & H5Lvisit \\
             & H5Lvisit\_by\_name \\

@@

/* Public wrappers for attribute callbacks */                                    
void *H5VLattr_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *attr_name, hid_t type_id, hid_t space_id, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
void *H5VLattr_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
herr_t H5VLattr_read(void *attr, hid_t connector_id, hid_t dtype_id, void *buf, hid_t dxpl_id, void **req);
herr_t H5VLattr_write(void *attr, hid_t connector_id, hid_t dtype_id, const void *buf, hid_t dxpl_id, void **req);
herr_t H5VLattr_get(void *obj, hid_t connector_id, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_close(void *attr, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for dataset callbacks */                                      
void *H5VLdataset_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t lcpl_id, hid_t type_id, hid_t space_id, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
void *H5VLdataset_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
herr_t H5VLdataset_read(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, void *buf, void **req);
herr_t H5VLdataset_write(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
herr_t H5VLdataset_get(void *dset, hid_t connector_id, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_specific(void *obj, hid_t connector_id, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_close(void *dset, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for file callbacks */                                         
void *H5VLfile_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
void *H5VLfile_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
herr_t H5VLfile_get(void *file, hid_t connector_id, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_specific(void *obj, hid_t connector_id, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_close(void *file, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for group callbacks */                                        
void *H5VLgroup_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t lcpl_id, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
void *H5VLgroup_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
herr_t H5VLgroup_get(void *obj, hid_t connector_id, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_specific(void *obj, hid_t connector_id, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_close(void *grp, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for link callbacks */
herr_t H5VLlink_create(H5VL_link_create_type_t create_type, void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
herr_t H5VLlink_move(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
herr_t H5VLlink_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);

/* Public wrappers for object callbacks */
void *H5VLobject_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
herr_t H5VLobject_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, const char *src_name, void *dst_obj, const H5VL_loc_params_t *loc_params2, const char *dst_name, hid_t connector_id, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
herr_t H5VLobject_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);

/* Public wrappers for named datatype callbacks */                               
void *H5VLdatatype_commit(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
void *H5VLdatatype_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
herr_t H5VLdatatype_get(void *dt, hid_t connector_id, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_specific(void *obj, hid_t connector_id, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_close(void *dt, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for asynchronous request callbacks */                         
herr_t H5VLrequest_wait(void *req, hid_t connector_id, uint64_t timeout, H5ES_status_t *status);
herr_t H5VLrequest_notify(void *req, hid_t connector_id, H5VL_request_notify_t cb, void *ctx);
herr_t H5VLrequest_cancel(void *req, hid_t connector_id);                 
herr_t H5VLrequest_specific(void *req, hid_t connector_id, H5VL_request_specific_t specific_type, va_list arguments);
herr_t H5VLrequest_optional(void *req, hid_t connector_id, va_list arguments);
herr_t H5VLrequest_free(void *req, hid_t connector_id);

/* Public wrappers for blob callbacks */                                         
herr_t H5VLblob_put(void *obj, hid_t connector_id, const void *buf, size_t size, void *blob_id, void *ctx);
herr_t H5VLblob_get(void *obj, hid_t connector_id, const void *blob_id, void *buf, size_t size, void *ctx);
herr_t H5VLblob_specific(void *obj, hid_t connector_id, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);

/* Public wrappers for generic 'optional' callback */                            
herr_t H5VLoptional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);

>>>>

         & H5Oopen\_by\_addr (deprecated) \\

@@

         & H5Oopen\_by\_token \\

@@

    get & H5Oget\_info1 (deprecated) \\
        & H5Oget\_info2 (deprecated) \\
        & H5Oget\_info3 \\

@@

             & H5Ovisit\_by\_name2 (deprecated) \\
             & H5Ovisit\_by\_name3 \\

@@

             & H5Ovisit2 (deprecated) \\
             & H5Ovisit3 \\

@@

        & H5Lget\_info1 (deprecated) \\
        & H5Lget\_info2 \\

@@

             & H5Literate1 (deprecated) \\
             & H5Literate2 \\
             & H5Literate\_by\_name1 (deprecated) \\
             & H5Literate\_by\_name2 \\
             & H5Lvisit1 (deprecated) \\
             & H5Lvisit2 \\
             & H5Lvisit\_by\_name1 (deprecated) \\
             & H5Lvisit\_by\_name2 \\

@@

/* Public wrappers for attribute callbacks */                                    
void *H5VLattr_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *attr_name, hid_t type_id, hid_t space_id, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
void *H5VLattr_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
herr_t H5VLattr_read(void *attr, hid_t connector_id, hid_t dtype_id, void *buf, hid_t dxpl_id, void **req);
herr_t H5VLattr_write(void *attr, hid_t connector_id, hid_t dtype_id, const void *buf, hid_t dxpl_id, void **req);
herr_t H5VLattr_get(void *obj, hid_t connector_id, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_optional(void *obj, hid_t connector_id, H5VL_attribute_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_close(void *attr, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for dataset callbacks */                                      
void *H5VLdataset_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t lcpl_id, hid_t type_id, hid_t space_id, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
void *H5VLdataset_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
herr_t H5VLdataset_read(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, void *buf, void **req);
herr_t H5VLdataset_write(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
herr_t H5VLdataset_get(void *dset, hid_t connector_id, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_specific(void *obj, hid_t connector_id, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_optional(void *obj, hid_t connector_id, H5VL_dataset_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_close(void *dset, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for file callbacks */                                         
void *H5VLfile_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
void *H5VLfile_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
herr_t H5VLfile_get(void *file, hid_t connector_id, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_specific(void *obj, hid_t connector_id, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_optional(void *obj, hid_t connector_id, H5VL_file_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_close(void *file, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for group callbacks */                                        
void *H5VLgroup_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t lcpl_id, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
void *H5VLgroup_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
herr_t H5VLgroup_get(void *obj, hid_t connector_id, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_specific(void *obj, hid_t connector_id, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_optional(void *obj, hid_t connector_id, H5VL_group_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_close(void *grp, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for link callbacks */
herr_t H5VLlink_create(H5VL_link_create_type_t create_type, void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
herr_t H5VLlink_move(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
herr_t H5VLlink_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_optional(void *obj, hid_t connector_id, H5VL_link_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);

/* Public wrappers for object callbacks */
void *H5VLobject_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
herr_t H5VLobject_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, const char *src_name, void *dst_obj, const H5VL_loc_params_t *loc_params2, const char *dst_name, hid_t connector_id, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
herr_t H5VLobject_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_optional(void *obj, hid_t connector_id, H5VL_object_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);

/* Public wrappers for named datatype callbacks */                               
void *H5VLdatatype_commit(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
void *H5VLdatatype_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
herr_t H5VLdatatype_get(void *dt, hid_t connector_id, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_specific(void *obj, hid_t connector_id, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_optional(void *obj, hid_t connector_id, H5VL_datatype_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_close(void *dt, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for connector/container introspection callbacks */            
H5_DLL herr_t H5VLintrospect_get_conn_cls(void *obj, hid_t connector_id, H5VL_get_conn_lvl_t lvl, const H5VL_class_t **conn_cls);                     
H5_DLL herr_t H5VLintrospect_opt_query(void *obj, hid_t connector_id, H5VL_subclass_t subcls, int opt_type, hbool_t *supported);

/* Public wrappers for asynchronous request callbacks */                         
herr_t H5VLrequest_wait(void *req, hid_t connector_id, uint64_t timeout, H5ES_status_t *status);
herr_t H5VLrequest_notify(void *req, hid_t connector_id, H5VL_request_notify_t cb, void *ctx);
herr_t H5VLrequest_cancel(void *req, hid_t connector_id);                 
herr_t H5VLrequest_specific(void *req, hid_t connector_id, H5VL_request_specific_t specific_type, va_list arguments);
herr_t H5VLrequest_optional(void *req, hid_t connector_id, H5VL_request_optional_t opt_type, va_list arguments);
herr_t H5VLrequest_free(void *req, hid_t connector_id);

/* Public wrappers for blob callbacks */                                         
herr_t H5VLblob_put(void *obj, hid_t connector_id, const void *buf, size_t size, void *blob_id, void *ctx);
herr_t H5VLblob_get(void *obj, hid_t connector_id, const void *blob_id, void *buf, size_t size, void *ctx);
herr_t H5VLblob_specific(void *obj, hid_t connector_id, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);
H5_DLL herr_t H5VLblob_optional(void *obj, hid_t connector_id, void *blob_id, H5VL_blob_optional_t opt_type, va_list arguments);

/* Public wrappers for token callbacks */                                        
H5_DLL herr_t H5VLtoken_cmp(void *obj, hid_t connector_id, const H5O_token_t *token1, const H5O_token_t *token2, int *cmp_value);
H5_DLL herr_t H5VLtoken_to_str(void *obj, H5I_type_t obj_type, hid_t connector_id, const H5O_token_t *token, char **token_str);
H5_DLL herr_t H5VLtoken_from_str(void *obj, H5I_type_t obj_type, hid_t connector_id, const char *token_str, H5O_token_t *token);

/* Public wrappers for generic 'optional' callback */                            
herr_t H5VLoptional(void *obj, hid_t connector_id, int op_type, hid_t dxpl_id, void **req, va_list arguments);
